### 2019-04-25 Appendices/AppendixE.tex
more spaces

\begin{equation}
\hat{H}(t) = \hat{H}(t+T)
\end{equation}

The Floquet theorem states that the eigenstates for the time evolution operator for one period, $\hat{U}(t+T,t)$ can be written as:

\begin{equation}
\label{FloquetMode}
\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
\end{equation}

Where $\ket{u_n(t+T)} = \ket{u_n(t)}$ is a periodic function, called Floquet mode, and $\epsilon_n$ is a real number known as the quasienergy. To show this, let $a_n(t)$ be the eigenvalue of $\ket{\psi_n(t)}$ under $\hat{U}(t+T,t)$, that is $\hat{U}(t+T,t)\ket{\psi_n(t)} = a_n(t)\ket{\psi_n(t)}$, then by multiplying this equation by $\hat{U}(t',t)$ from the left and using the periodicity of the Hamiltonian in $\hat{U}(t',t) = \hat{U}(t'+T,t+T)$ we obtain:

\begin{align*}
\hat{U}(t'+T,t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
\hat{U}(t'+T,t) \hat{U}(t,t')\hat{U}(t',t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
\hat{U}(t'+T,t') \ket{\psi_n(t')} &= a_n(t)\ket{\psi_n(t')}
\end{align*}

Which means that $a_n(t') = a_n(t)$, so the eigenvalue does not depend on time, and since it is an eigenvalue of an unitary operator it can be written as $a_n = a_n(t) = e^{-i\epsilon_nT}$ for certain real number $\epsilon_n$. Therefore, we have

\begin{align*}
\ket{\psi_n(t+T)} &= e^{-i\epsilon_nT} \ket{\psi_n(t)} \rightarrow \\
\ket{\psi_n(t)} &= e^{-i\epsilon_nt} \ket{u_n(t)}
\end{align*}

For $\ket{u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{u_n(t+T)}$, and this proves the theorem. The states $\ket{\psi_n(t)}$ are called Floquet states and are solutions of the time dependent Schr\"{o}dinger equation $i\text{d}_t\ket{\psi_n(t)} = \hat{H}(t)\ket{\psi_n(t)}$. The time evolution operator can be written as:

\begin{equation}
\hat{U}(t_2,t_1) = \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)}
\end{equation}

Therefore the time evolution of a superposition of Floquet states will be determined by two different contributions:

\begin{itemize}
\item The periodic evolution of the superposing Floquet modes. This is called micromotion.
\item The non-periodic dephasing due to the factor $e^{-i\epsilon_n(t_2-t_1)}$ depending on the quasienergies $\epsilon_n$.
\end{itemize}

It is interesting to study these two time dependencies separately. With his purpose we define the micromotion operator and the Floquet Hamiltnian. The micromotion operator is defined as:
\begin{equation}
\hat{U}_F(t_2,t_1) \equiv \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)}
\end{equation}
so that $\ket{u_n(t_2)} = \hat{U}_F(t_2,t_1)\ket{u_n(t_1)}$, i.e. it is responsible of the periodic time evolution intrinsic of the Floquet modes. On the other hand, the Floquet Hamiltonian $\hat{H}_{t_0}^F$ is a time-independent Hamiltonian defined such that:
\begin{equation}
e^{-iT\hat{H}_{t_0}^F} \equiv \hat{U}(t_0+T,t_0)
\end{equation}
or equivalently:
\begin{equation}
e^{-it\hat{H}_{t_0}^F} = \sum_n e^{-i\epsilon_nt}\ket{u_n(t_0)}\bra{u_n(t_0)}
\end{equation}
this Hamiltonian will time-evolve states by adding a phase $e^{-i\epsilon_n(t_2-t_1)}$ to the correspondent fixed-time modes. The full time evolution operator is a combination of both time evolutions:
\begin{align*}
\hat{U}(t_2,t_1) &= \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)} = \\
&\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_2)} \right)\left( \sum_n\ket{u_n(t_2)}\bra{u_n(t_1)}\right) = \\
&\left( \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)} \right)\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_1)}\bra{u_n(t_1)} \right)
\end{align*}
That is:
\begin{equation}
\hat{U}(t_2,t_1) = e^{-i(t_2-t_1)\hat{H}_{t_2}^F}\hat{U}_F(t_2,t_1) = \hat{U}_F(t_2,t_1)e^{-i(t_2-t_1)\hat{H}_{t_1}^F}
\end{equation}

@@

\begin{equation}
\left[ \hat{H}-i\text{d}_t\right] \ket{u_n(t)} = \epsilon_n\ket{u_n(t)}
\end{equation}

This can be regarded as an eigenvalue problem in the space $\mathcal{F}=\mathcal{H}\otimes\mathcal{L}_T$, where $\mathcal{L}_T$ is the space of square integrable T-periodic functions. The operator $\hat{Q} = \hat{H}-i\text{d}_t$ acting on $\mathcal{F}$ is referred to as the quasienergy operator. States in the extended Hilbert space (that is, a state plus its periodic time dependence) is usually denoted as $\ket{u}\rangle$, and the inner product in this space is defined as:

\begin{equation}
\langle \bra{u}\ket{v} \rangle = \frac{1}{T}\int_0^T \text{d}t \bra{u(t)}\ket{v(t)}
\end{equation}

An orthonormal basis for the extended Hilbert space can be obtained as the direct product of an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$. A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, where $m$ is usually referred to as the photon number. Then, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$. In this basis, the quasienergy operator has matrix elements:

\begin{align}
\langle \bra{\alpha' m'}\hat{Q}\ket{\alpha m} \rangle &= \frac{1}{T}\int_0^T \text{d}t e^{-im'\omega t}\bra{\alpha'} \hat{H}(t)-i\hbar\text{d}_t \ket{\alpha}e^{im\omega t} = \nonumber \\
&= \bra{\alpha'} \hat{H}_{m'-m} \ket{\alpha} + \delta_{m'm}\delta_{\alpha' \alpha}m\hbar\omega \label{QOmatelem}
\end{align}

Where
\begin{equation}
\hat{H}_m = \frac{1}{T}\int_0^T \text{d}t e^{-im\omega t}\hat{H}(t) 
\end{equation}
is the Fourier transform of the Hamiltonian. Now, a Floquet state $\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}$ can be expanded as $\ket{u_n(t)} = \sum_m e^{im\omega t}\ket{u_{nm}}$, using \ref{QOmatelem} and projecting onto the \textit{m}th Fourier mode we can rewrite the Scr\"{o}dinger equation as:

@@

\begin{align}
\hat{H}(t) \rightarrow \hat{H}'(t) &= \hat{U}^{\dagger}(t)\hat{H}(t)\hat{U}(t) - i\hat{U}^{\dagger}(t)\text{d}_t\hat{U}(t) \\
\ket{\psi(t)} \rightarrow \ket{\psi'(t)} &= \hat{U}^{\dagger}(t)\ket{\psi(t)}
\end{align}

The goal is to find $\hat{U}(t)$ such that the transformed quasienergy operator $\hat{Q}'$ is block diagonal in the photon number. Using \ref{QOmatelem} we notice that this requirement is equivalent to the requirement that the transformed Hamiltonian $\hat{H}'(t)$ is time independent.

>>>>

\begin{equation}
\hat{H}(t) = \hat{H}(t+T)
\end{equation}
The Floquet theorem states that the eigenstates for the time evolution operator for one period, $\hat{U}(t+T,t)$ can be written as:

\begin{equation}
\label{FloquetMode}
\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
\end{equation}
Where $\ket{u_n(t+T)} = \ket{u_n(t)}$ is a periodic function, called Floquet mode, and $\epsilon_n$ is a real number known as the quasienergy. To show this, let $a_n(t)$ be the eigenvalue of $\ket{\psi_n(t)}$ under $\hat{U}(t+T,t)$, that is $\hat{U}(t+T,t)\ket{\psi_n(t)} = a_n(t)\ket{\psi_n(t)}$, then by multiplying this equation by $\hat{U}(t',t)$ from the left and using the periodicity of the Hamiltonian in $\hat{U}(t',t) = \hat{U}(t'+T,t+T)$ we obtain:

\begin{align*}
\hat{U}(t'+T,t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
\hat{U}(t'+T,t) \hat{U}(t,t')\hat{U}(t',t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
\hat{U}(t'+T,t') \ket{\psi_n(t')} &= a_n(t)\ket{\psi_n(t')}
\end{align*}
Which means that $a_n(t') = a_n(t)$, so the eigenvalue does not depend on time, and since it is an eigenvalue of an unitary operator it can be written as $a_n = a_n(t) = e^{-i\epsilon_nT}$ for certain real number $\epsilon_n$. Therefore, we have

\begin{align*}
\ket{\psi_n(t+T)} &= e^{-i\epsilon_nT} \ket{\psi_n(t)} \rightarrow \\
\ket{\psi_n(t)} &= e^{-i\epsilon_nt} \ket{u_n(t)}
\end{align*}
For $\ket{u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{u_n(t+T)}$, and this proves the theorem. The states $\ket{\psi_n(t)}$ are called Floquet states and are solutions of the time dependent Schr\"{o}dinger equation $i\text{d}_t\ket{\psi_n(t)} = \hat{H}(t)\ket{\psi_n(t)}$. The time evolution operator can be written as:

\begin{equation}
\hat{U}(t_2,t_1) = \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)}
\end{equation}
Therefore the time evolution of a superposition of Floquet states will be determined by two different contributions:

\begin{itemize}
\item The periodic evolution of the superposing Floquet modes. This is called micromotion.
\item The non-periodic dephasing due to the factor $e^{-i\epsilon_n(t_2-t_1)}$ depending on the quasienergies $\epsilon_n$.
\end{itemize} 
It is interesting to study these two time dependencies separately. With his purpose we define the micromotion operator and the Floquet Hamiltnian. The micromotion operator is defined as:
\begin{equation}
\hat{U}_F(t_2,t_1) \equiv \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)}
\end{equation}
so that $\ket{u_n(t_2)} = \hat{U}_F(t_2,t_1)\ket{u_n(t_1)}$, i.e. it is responsible of the periodic time evolution intrinsic of the Floquet modes. On the other hand, the Floquet Hamiltonian $\hat{H}_{t_0}^F$ is a time-independent Hamiltonian defined such that:
\begin{equation}
e^{-iT\hat{H}_{t_0}^F} \equiv \hat{U}(t_0+T,t_0)
\end{equation}
or equivalently:
\begin{equation}
e^{-it\hat{H}_{t_0}^F} = \sum_n e^{-i\epsilon_nt}\ket{u_n(t_0)}\bra{u_n(t_0)}
\end{equation}
this Hamiltonian will time-evolve states by adding a phase $e^{-i\epsilon_n(t_2-t_1)}$ to the correspondent fixed-time modes. The full time evolution operator is a combination of both time evolutions:
\begin{align*}
\hat{U}(t_2,t_1) &= \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)} = \\
&\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_2)} \right)\left( \sum_n\ket{u_n(t_2)}\bra{u_n(t_1)}\right) = \\
&\left( \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)} \right)\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_1)}\bra{u_n(t_1)} \right)
\end{align*}
That is:
\begin{equation}
\hat{U}(t_2,t_1) = e^{-i(t_2-t_1)\hat{H}_{t_2}^F}\hat{U}_F(t_2,t_1) = \hat{U}_F(t_2,t_1)e^{-i(t_2-t_1)\hat{H}_{t_1}^F}
\end{equation}

@@

\begin{equation}
\left[ \hat{H}-i\text{d}_t\right] \ket{u_n(t)} = \epsilon_n\ket{u_n(t)}
\end{equation}
This can be regarded as an eigenvalue problem in the space $\mathcal{F}=\mathcal{H}\otimes\mathcal{L}_T$, where $\mathcal{L}_T$ is the space of square integrable T-periodic functions. The operator $\hat{Q} = \hat{H}-i\text{d}_t$ acting on $\mathcal{F}$ is referred to as the quasienergy operator. States in the extended Hilbert space (that is, a state plus its periodic time dependence) is usually denoted as $\ket{u}\rangle$, and the inner product in this space is defined as:

\begin{equation}
\langle \bra{u}\ket{v} \rangle = \frac{1}{T}\int_0^T \text{d}t \bra{u(t)}\ket{v(t)}
\end{equation}
An orthonormal basis for the extended Hilbert space can be obtained as the direct product of an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$. A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, where $m$ is usually referred to as the photon number. Then, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$. In this basis, the quasienergy operator has matrix elements:

\begin{align}
\langle \bra{\alpha' m'}\hat{Q}\ket{\alpha m} \rangle &= \frac{1}{T}\int_0^T \text{d}t e^{-im'\omega t}\bra{\alpha'} \hat{H}(t)-i\hbar\text{d}_t \ket{\alpha}e^{im\omega t} = \nonumber \\
&= \bra{\alpha'} \hat{H}_{m'-m} \ket{\alpha} + \delta_{m'm}\delta_{\alpha' \alpha}m\hbar\omega \label{QOmatelem}
\end{align}
Where
\begin{equation}
\hat{H}_m = \frac{1}{T}\int_0^T \text{d}t e^{-im\omega t}\hat{H}(t) 
\end{equation}
is the Fourier transform of the Hamiltonian. Now, a Floquet state $\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}$ can be expanded as $\ket{u_n(t)} = \sum_m e^{im\omega t}\ket{u_{nm}}$, using \ref{QOmatelem} and projecting onto the \textit{m}th Fourier mode we can rewrite the Scr\"{o}dinger equation as:

@@

\begin{align}
\hat{H}(t) \rightarrow \hat{H}'(t) &= \hat{U}^{\dagger}(t)\hat{H}(t)\hat{U}(t) - i\hat{U}^{\dagger}(t)\text{d}_t\hat{U}(t) \\
\ket{\psi(t)} \rightarrow \ket{\psi'(t)} &= \hat{U}^{\dagger}(t)\ket{\psi(t)}
\end{align}
The goal is to find $\hat{U}(t)$ such that the transformed quasienergy operator $\hat{Q}'$ is block diagonal in the photon number. Using \ref{QOmatelem} we notice that this requirement is equivalent to the requirement that the transformed Hamiltonian $\hat{H}'(t)$ is time independent.

### 2019-04-25 Chapters/Chap3/HWithSoi.tex
more spaces

\begin{equation}
\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
\end{equation}

The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI. 
In this case the hopping amplitudes are:

@@

\begin{align}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
\end{align}

Using $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$:

\begin{align*}
&(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) = \\ 
&\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})
\end{align*}

The term proportional to $t_0^2$ will lead to the modified exchange interaction, as in the previous section. The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction and the term proportional to $\bs{\Delta}_{ij}^2$ will lead to the pseudodipolar interaction.

@@

\begin{align*}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ji}\cdot\bs{\sigma}_{\sigma_3, \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) + \\
&+\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \\
&(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\cdot\bs{S}_j + 2it_0\bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} \left\{ J_{ij}\bs{S}_i\cdot\bs{S}_j +\bs{D}_{ij}\cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j \right\}
\end{align*}

Where we used relations \ref{SpinRel1}, \ref{SpinRel2} and \ref{SpinRel3}. We have:

\begin{align}
J_{ij} &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
\bs{D}_{ij} &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI} \\
\Gamma_{ij}^{\alpha \beta} &= (\delta_{\alpha \beta} \bs{\Delta}_{ij}^2 - 2\Delta_{ij}^\alpha\Delta_{ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align}

We can see that since we only considered NN hopping processes, all the terms in the spin Hamiltonian are renormalized in the same way by the laser field (as in \cite{Stepanov2017}). In order to obtain different dependencies with the field we should consider NNN hopping processes.

>>>>

\begin{equation}
\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
\end{equation}
The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI. 
In this case the hopping amplitudes are:

@@

\begin{align}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
\end{align}
Using $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$:

\begin{align*}
&(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) = \\ 
&\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})
\end{align*}
The term proportional to $t_0^2$ will lead to the modified exchange interaction, as in the previous section. The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction and the term proportional to $\bs{\Delta}_{ij}^2$ will lead to the pseudodipolar interaction.

@@

\begin{align*}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ji}\cdot\bs{\sigma}_{\sigma_3, \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) + \\
&+\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \\
&(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\cdot\bs{S}_j + 2it_0\bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} \left\{ J_{ij}\bs{S}_i\cdot\bs{S}_j +\bs{D}_{ij}\cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j \right\}
\end{align*}
Where we used relations \ref{SpinRel1}, \ref{SpinRel2} and \ref{SpinRel3}. We have:

\begin{align}
J_{ij} &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
\bs{D}_{ij} &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI} \\
\Gamma_{ij}^{\alpha \beta} &= (\delta_{\alpha \beta} \bs{\Delta}_{ij}^2 - 2\Delta_{ij}^\alpha\Delta_{ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align}
We can see that since we only considered NN hopping processes, all the terms in the spin Hamiltonian are renormalized in the same way by the laser field (as in \cite{Stepanov2017}). In order to obtain different dependencies with the field we should consider NNN hopping processes.
